---
output: 
  html_document:
    keep_md: true
---

# OSS RL Aug-Sep 2017 analysis on D36

## Run statistical test on *Decline* for confirmation the increased of *D36*

```{r adjust_directory_if_needed, include=FALSE}
# Initialise Project
# Uncomment lines below if rmd file is placed in a subdirectory
# library(knitr)
# opts_knit$set(root.dir = normalizePath('../')) 
```

```{r load_project, include=FALSE}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and coe in lib directory
# 4. Load data in data directory
# 5. Run data manipulations in munge directory 

rm(list = ls()) # optionally refresh workspace
library(ProjectTemplate); load.project()
rl_os <- subset(rl_os, month %in% c('y201708', 'y201709'))
rm(thaiMaps)
```

Test of independent (difference) : result & month
```{r chiq_test_independent_result_month, echo=FALSE}
group <- 'month'
attrib <- 'result'
t <- table(rl_os[[group]], rl_os[[attrib]])
cat(paste0('Table of ', attrib, ' by ', group))
print(t)
writeLines('')
cat(paste0('Percent contribution of ', attrib, ' by ', group))
prop.table(t, 1)*100
chisq.test(t)
i <- chisq.test(t)
i_p <- i$p.value
if (i_p <= 0.05) {
    cat(paste0(group,' and ',attrib, ' are dependent'))
} else {
    cat(paste0(group,' and ',attrib, ' are independent'))
}
# mosaicplot(t)
# assocplot(t)
rm(list = c('group', 'attrib', 't', 'i', 'i_p'))
```

Test of each result proportion by month
```{r prop_test_each_result_month, echo=FALSE}
all_result <- unique(rl_os$result)
for (i in seq_along(all_result)) {
    t <- table(rl_os$month, ifelse(rl_os$result == all_result[i], 
                                   all_result[i], paste0('Not ', all_result[i])))
        cat(paste0("Contingency Table of ", all_result[i]))
        print(t)
        cat("\n% Proportion")
        print(prop.table(t, 1)*100)
        print(prop.test(t))
}
rm(list = c('i', 't', 'all_result'))
```

From proportion test (z-test) of each *result*, the *D* effect the % approval rate most. Then do more test on each *D*

Number of top 5 *D*
```{r top5_d, echo=FALSE}
top5 <- rl_os %>%
        filter(result == 'D') %>%
        group_by(month, result_description) %>%
        summarise(n = n()) %>%
        spread(month, n) %>%
        top_n(5)
print(top5)
```

% Proportion of top 5 *D*
```{r per_top5_d, echo=FALSE}
rl_os %>%
    filter(result == 'D') %>%
    group_by(month, result_description) %>%
    summarise(n = n()) %>%
    mutate(per_finl = prop.table(n)*100) %>%
    select(month, result_description, per_finl) %>%
    spread(key = month, value = per_finl) %>%
    top_n(5)
```

Proportion test top 5 *D* by each *result description*
```{r test_top5_result_desc, echo=FALSE0}
top5_desc <- top5$result_description
d <- rl_os %>% filter(result == 'D')
for (i in seq_along(top5_desc)) {
    t <- table(d$month, ifelse(d$result_description == top5_desc[i], 
                                   top5_desc[i], paste0('Not ', top5_desc[i])))
        cat(paste0("Contingency Table of ", top5_desc[i]))
        print(t)
        cat("\n% Proportion")
        print(prop.table(t, 1)*100)
        print(prop.test(t))
}
rm(list = c("top5_desc", "top5", "d", "t", "i"))
```

From statistic test there are 3 reasons that statistically significant
* D09 ประมาณการรายได้ไม่เพียงพอต่อการชำระหนี้, 201709 < 201708
* D30 ภาระหนี้ใน NCB สูง ออกจดหมายแจ้งลูกค้า, 201709 > 201708
* D36 สินเชื่อบุคคลเกินเกณฑ์ BOT ออกจดหมาย NCB, 201709 > 201708

**EDA on D09**
```{r EDA_D09, echo=FALSE}
rl_os %>%
    ggplot(aes(x = monthly_salary, fill = factor(month))) +
    geom_histogram(position = 'identity', alpha = 0.5,
        breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000)) +
    scale_x_continuous(breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Histogram plot of finalized - income by month")

rl_os %>%
    ggplot(aes(x = monthly_salary, color = factor(month))) +
    geom_density() +
    scale_x_log10(limits = c(5000, 200000),
                  breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Density plot of finalized - income by month")

rl_os %>%
    filter(result_description == "D09") %>%
    ggplot(aes(x = monthly_salary, fill = factor(month))) +
    geom_histogram(position = 'identity', alpha = 0.5,
        breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000)) +
    scale_x_continuous(breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Histogram plot of D09 - income by month")

rl_os %>%
    filter(result_description == "D09") %>%
    ggplot(aes(x = monthly_salary, color = factor(month))) +
    geom_density() +
    scale_x_log10(limits = c(5000, 200000),
                  breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Density plot of D09 - income by month")

```

All finalized app for income range 10-12k, 12-15k, 15-20k, 20-30k decreased
while 30-40k, 40-50k maintain.

As per density plot, the D09 at income range 15-20k, the spike on 201709 flatterned down compare to 201708. That's the reason of decreasing *D09*

**EDA on D30**
```{r EDA_D30, echo=FALSE}

rl_os %>%
    filter(result_description == "D30") %>%
    ggplot(aes(x = monthly_salary, fill = factor(month))) +
    geom_histogram(position = 'identity', alpha = 0.5,
        breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000)) +
    scale_x_continuous(breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Histogram plot of D30 - income by month")

rl_os %>%
    filter(result_description == "D30") %>%
    ggplot(aes(x = monthly_salary, color = factor(month))) +
    geom_density() +
    scale_x_log10(limits = c(5000, 200000),
                  breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Density plot of D30 - income by month")

```

**EDA on D36**
```{r EDA_D36, echo=FALSE}

rl_os %>%
    filter(result_description == "D36") %>%
    ggplot(aes(x = monthly_salary, fill = factor(month))) +
    geom_histogram(position = 'identity', alpha = 0.5,
        breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000)) +
    scale_x_continuous(breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Histogram plot of D36 - income by month")

rl_os %>%
    filter(result_description == "D36") %>%
    ggplot(aes(x = monthly_salary, color = factor(month))) +
    geom_density() +
    scale_x_log10(limits = c(5000, 200000),
                  breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                  labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k')) +
    ggtitle(label = "Density plot of D36 - income by month")

```

For *D36* have high spike, knock down, on income ~16k and 22k.

# Predictive modle on D36, use data from 201709 onwards
Spliting data -> train (70%), test(30%)
Split with respect to proportion of d36_flag 
```{r D36_split_data, echo=FALSE}
df <- rl_os %>%
    filter(substr(month, 2, 7) >= 201709) %>%
    mutate(d36_flag = ifelse(result_description == "D36", TRUE, FALSE))

library(caTools)
set.seed(59)
split_idx <- sample.split(df$d36_flag, SplitRatio = 0.7)
train <- df[split_idx,]
test <- df[!split_idx,]

detach(package:caTools)
rm(split_idx)
```

## Train data base line 
Use naive guess, predict all according to the most proportion in train data.
```{r baseline_naive_guess, echo=FALSE}
cat("Proportion of d36_flag in train data")
prop.table(table(train$d36_flag))

pred <- rep(FALSE, dim(test)[1])
writeLines("\nPrediction (all FALSE) - test data")
prop.table(table(test$d36_flag, pred))
```

If predict all as *FALSE* , the **accuracy = 0.96761** as base line for new model.

## Logit Model
```{r model_logit_threshold, echo=FALSE}
logit_1 <- glm(d36_flag ~ monthly_salary, 
               data = train, family = 'binomial')
logit_2 <- update(logit_1, . ~ . + age)
logit_3 <- update(logit_2, . ~ . + monthly_salary:age)
# the logit_3 experience overfitted problems

# logit_4 <- glm(d36_flag ~ log10(monthly_salary), 
#               data = subset(train, monthly_salary > 0), 
#               family = 'binomial')
# logit_4 not significant


# Choose model based on least AIC
logit_1$aic; logit_2$aic; logit_3$aic

pred <- predict(logit_3, newdata = test, type = 'response')

# choose plot ROCR Curve & calculate 'AUC' (Area Under Curved)
library(ROCR)
rocrPred <- prediction(pred, test$d36_flag)
rocrPerf <- performance(rocrPred, 'tpr', 'fpr')
plot(rocrPerf, colorize = TRUE,
     print.cutoffs.at = seq(0, 0.05, 0.01),
     main = "ROCR curved of logit model")
writeLines("AUC of logit model")
print(performance(rocrPred, 'auc')@y.values)
```
As *ROCR* curved shown threshold for P(Y = 1) best at 0.02.
```{r logit_accuracy, echo=FALSE}
table(test$d36_flag, pred >= 0.06)
```

The logit model accuracy = (2191+154)/(2191+154+3306+30) = 0.9082
worst than the base-line. T.T

## Decision Tree
```{r decision_tree, echo=FALSE}
library(rpart)
library(rpart.plot)
tree <- rpart(d36_flag ~ age + region2 + monthly_salary,
              data = train,
              method = 'class')

```

