---
output: 
  html_document:
    keep_md: false
---

# OSS RL Jan-Sep 2017 analysis

```{r adjust_directory_if_needed, include=FALSE}
# Initialise Project
# Uncomment lines below if rmd file is placed in a subdirectory
# library(knitr)
# opts_knit$set(root.dir = normalizePath('../')) 
```

```{r filter_mgr, include=FALSE}
# 1. Set options in config/global.dcf
# 2. Load packages listed in config/global.dcf
# 3. Import functions and coe in lib directory
# 4. Load data in data directory
# 5. Run data manipulations in munge directory 

# rm(list = ls()) # optionally refresh workspace
# library(ProjectTemplate); load.project()
print("Report for Mgr : ")
print(mgr_code)
df <- rl_os %>% filter(rl_os$X1m == mgr_code)
```             

## Key number summary
```{r table_summary_result, echo=FALSE, message=FALSE}
df %>%
    group_by(month) %>%
    summarise(finalize = n(), appr = sum(appr), 
              loansize_amt = sum(approve_amount), fdd_amt = sum(fdd)) %>%
    gather(key = kpi, value = value, -month) %>%
    spread(key = month, value = value) %>%
    mutate(kpi = factor(kpi, levels = c('finalize', 'appr', 
                                        'loansize_amt', 'fdd_amt'))) %>%
    arrange(kpi) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

## Key Kpi by Month
### Approved Performance

% Approval rate, Avg Loansize, Avg FDD, % Early 60D
```{r key_kpi_summary, echo=FALSE, message=FALSE}
df %>%
    group_by(month) %>%
    summarise(per_appr = sum(appr)/n()*100, 
              avg_loansize = sum(approve_amount)/sum(appr),
              avg_fdd = sum(fdd)/sum(appr), 
              per_early60D = sum(vxandearly60)/sum(appr)*100) %>%
    gather(key = kpi, value = value, -month) %>%
    spread(key = month, value = value) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

### Finalized Performance
Number of Appr, Decline, Cancel
```{r appr_decline_cancel_table, echo=FALSE, message=FALSE}
df %>%
    group_by(month, result) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Percent of Appr, Decline, Cancel
```{r appr_decline_cancel_percent_table, echo=FALSE, message=FALSE}
# table of percent
df %>%
    group_by(month, result) %>%
    summarise(finl = n()) %>%
    mutate(per_finl = prop.table(finl)*100) %>%
    select(month, result, per_finl) %>%
    spread(key = month, value = per_finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Top Decline Reason
```{r top_decline, echo=FALSE, message=FALSE, message=FALSE}
df %>%
    filter(result == 'D') %>%
    group_by(month, result_description) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    top_n(5) %>%
    left_join(reason_desc, by = c('result_description' = 'reason_code')) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Percent top Decline Reason
```{r top_decline_percent, echo=FALSE, message=FALSE, message=FALSE}
df %>%
    filter(result == 'D') %>%
    group_by(month, result_description) %>%
    summarise(finl = n()) %>%
    mutate(per_finl = prop.table(finl)*100) %>%
    select(month, result_description, per_finl) %>%
    spread(key = month, value = per_finl) %>%
    top_n(5) %>%
    left_join(reason_desc, by = c('result_description' = 'reason_code')) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Top Cancel Reason
```{r top_cancel, echo=FALSE, message=FALSE, message=FALSE}
df %>%
    filter(result == 'C') %>%
    group_by(month, result_description) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    top_n(5) %>%
    left_join(reason_desc, by = c('result_description' = 'reason_code')) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Percent top Cancel Reason
```{r top_cancel_percent, echo=FALSE, message=FALSE, message=FALSE}
df %>%
    filter(result == 'C') %>%
    group_by(month, result_description) %>%
    summarise(finl = n()) %>%
    mutate(per_finl = prop.table(finl)*100) %>%
    select(month, result_description, per_finl) %>%
    spread(key = month, value = per_finl) %>%
    top_n(5) %>%
    left_join(reason_desc, by = c('result_description' = 'reason_code')) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Customer income range table
```{r cust_inc_table, echo=FALSE, message=FALSE}
df %>%
    filter(income_range %in% c('10,000-14,999', '15,000-19,999', 
                               '20,000-29,999', '30,000 up')) %>%
    group_by(month, income_range) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Customer income historgram for last 4 month, (interactive graph)
```{r cust_inc_histogram, echo=FALSE, message=FALSE}
month_data <- unique(df$month)
month_data_length <- length(month_data)
last_4_month_idx <- ifelse(month_data_length <= 4, 1, month_data_length - 3)

library(plotly)
p <- df %>%
    filter(monthly_salary > 1, 
           month %in% month_data[last_4_month_idx:month_data_length]) %>%
    ggplot(aes(x = monthly_salary, fill = factor(month), 
               color = factor(month))) + 
               geom_histogram(position = 'identity', alpha = 0.5,
                breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000)) +
    scale_x_continuous(breaks = c(10000, 12000, 15000, 20000, 30000, 40000, 50000),
                       labels = c('10k', '12k', '15k', '20k', '30k', '40k', '50k'))
ggplotly(p)

rm(list = c('month_data', 'month_data_length', 'last_4_month_idx'))
```

Customer income density (mountain)
```{r cust_inc_density, echo=FALSE, message=FALSE}
library(ggridges)
df %>%
    filter(monthly_salary > 1) %>%
    ggplot(aes(x = monthly_salary, y = month, group = month)) + 
    geom_density_ridges(rel_min_height = 0.01) +
    scale_x_log10(breaks = c(10000, 15000, 20000, 30000, 40000, 50000), 
                  labels = c('10k', '15k', '20k', '30k', '40k', '50k'),
                  limits = c(5000, 150000))
```

Customer age range table
```{r cust_age_table, echo=FALSE, message=FALSE}
df %>%
    group_by(month, cus_age_range) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Customer age historgram for last 4 month, (interactive graph)
```{r cust_age_histogram, echo=FALSE, message=FALSE}
month_data <- unique(df$month)
month_data_length <- length(month_data)
last_4_month_idx <- ifelse(month_data_length <= 4, 1, month_data_length - 3)

library(plotly)
p <- df %>%
    filter(month %in% month_data[last_4_month_idx:month_data_length]) %>%
    ggplot(aes(x = age, fill = factor(month), color = factor(month))) + 
               geom_histogram(position = 'identity', alpha = 0.5,
                              breaks = c(20, 26, 30, 40, 50, 60, Inf))
ggplotly(p)

rm(list = c('month_data', 'month_data_length', 'last_4_month_idx'))
```

Customer age density (mountain)

```{r cust_age_density, echo=FALSE, message=FALSE}
library(ggridges)
df %>%
    ggplot(aes(x = age, y = month, group = month)) + 
    geom_density_ridges(stat = 'binline', binwidth = 1) +
    scale_x_continuous(breaks = seq(20, 60, 5), limits = c(18, 62))
```

Customer region table
```{r cust_region_table, echo=FALSE, message=FALSE}
df %>%
    group_by(month, region2) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Percent Customer region
```{r cust_region_percent_table, echo=FALSE, message=FALSE}
# table of percent
df %>%
    group_by(month, region2) %>%
    summarise(finl = n()) %>%
    mutate(per_finl = prop.table(finl)*100) %>%
    select(month, region2, per_finl) %>%
    spread(key = month, value = per_finl) %>%
    kable(format = 'html', digits = 2,
          format.args = list(decimal.mark = ".", big.mark = ",")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = FALSE, position = 'left')
```

Customer province map, (interactive map)
```{r cust_province_map, echo=FALSE, message=FALSE}
# summarise finalized by month, province, tt_finalized
finl_province <- df %>%
    group_by(province) %>%
    summarise(tt_finl = n())
finl_mth_province <- df %>%
    group_by(month, province) %>%
    summarise(finl = n()) %>%
    spread(key = month, value = finl) %>%
    left_join(finl_province)
rm(finl_province)

# create shape file with ktc data
thaiMaps_ktc <- thaiMaps
thaiMaps_ktc@data <- left_join(x = thaiMaps_ktc@data, y = finl_mth_province,
                               by = c("PROV_NAMT" = "province"))
rm(finl_mth_province)

library(leaflet)
# create color palette function by defined bins data  
pal_fun <- colorBin("YlOrRd", domain = thaiMaps_ktc$tt_finl, 
                    bins = c(0, 250, 500, 1000, 2000, 5000, 10000, Inf))

# Label for interactive pop up
labels <- sprintf("<strong>%s</strong><br/>total finalized : %g", 
                  thaiMaps_ktc$PROV_NAMT, 
                  thaiMaps_ktc$tt_finl) %>% 
    lapply(htmltools::HTML)

# Plot maps
leaflet(data = thaiMaps_ktc) %>%
    addTiles() %>%
    addPolygons(
      fillColor = ~pal_fun(tt_finl),
      weight = 2,
      opacity = 1,
      color = "white",
      dashArray = "3",
      fillOpacity = 0.7,
      highlight = highlightOptions(
        weight = 5,
        color = "#666",
        dashArray = "",
        fillOpacity = 0.7,
        bringToFront = TRUE),
      label = labels,
      labelOptions = labelOptions(
          style = list("font-weight" = "normal", padding = "3px 8px"),
          textsize = "15px",
          direction = "auto")) %>%
    addLegend(pal = pal_fun, values = ~tt_finl, opacity = 0.7, title = NULL,
    position = "bottomright")

```
